Attributions for Poverty in Post-Socialist Countries

### 2014-03-30 article2013.Rmd
last checks. korjasin postsos maiden lkm 21een 22sta

The study utilizes the data from the second wave of Life in Transition Survey[^***2] (LiTS2), conducted by European Bank of Development and Reconstruction (EBRD) and  World Bank in 2010. The analyses cover 22 post-socialist countries and 5 Western European countries. The survey was collected using a two-stage clustered stratified sampling procedure to select the households that were included in the sample (for more detailed description of sampling and data collection, see EBRD 2011). The survey had a special focus on how people’s lives were affected by the global economic crises and its aftermath.

@@

We target our analyses at 22 post-socialist countries and use five Western European countries as references in descriptive analyses (see Figure 2). Our selection on 22 post-socialist countries includes Czech Republic, Estonia, Hungary, Bulgaria, Latvia, Lithuania, Poland, Slovakia, Slovenia, Romania from Central Eastern Europe (CEE), and Armenia, Azerbaijan, Belarus, Georgia, Kazakhstan, Kyrgyzstan, Moldova, Tajikistan, Ukraine, Uzbekistan and Russia from Commonwealth of Independent States (CIS)[^***]. Of Western European countries we have included France, Germany, Italy, United Kingdom and Sweden as references.

>>>>

The study utilizes the data from the second wave of Life in Transition Survey[^***2] (LiTS2), conducted by European Bank of Development and Reconstruction (EBRD) and  World Bank in 2010. The analyses cover 21 post-socialist countries and 5 Western European countries. The survey was collected using a two-stage clustered stratified sampling procedure to select the households that were included in the sample (for more detailed description of sampling and data collection, see EBRD 2011). The survey had a special focus on how people’s lives were affected by the global economic crises and its aftermath.

@@

We target our analyses at 21 post-socialist countries and use five Western European countries as references in descriptive analyses (see Figure 2). Our selection on 21 post-socialist countries includes Czech Republic, Estonia, Hungary, Bulgaria, Latvia, Lithuania, Poland, Slovakia, Slovenia, Romania from Central Eastern Europe (CEE), and Armenia, Azerbaijan, Belarus, Georgia, Kazakhstan, Kyrgyzstan, Moldova, Tajikistan, Ukraine, Uzbekistan and Russia from Commonwealth of Independent States (CIS)[^***]. Of Western European countries we have included France, Germany, Italy, United Kingdom and Sweden as references.
